Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-28 proposal/prop.tex
prop.tex \subsection{Proposed Activity I: Quantum States as Interactive Processes} Add citations...

The early formalization of the process of computing using Turing
machines~\cite{Turing_1937} or the
$\lambda$-calculus~\cite{Barendregt:Lambda} viewed a computation as
realizing a mathematical function. From our perspective, the most
important consequence of this view is that the properties of the
computed function existed independently of any observation,
calculation, or interaction. For example, a function is
\emph{injective} or not independently of any observation. An agent can
only interact with the computation by asking questions regarding its
input-output behavior and although such interaction would reveal
fragments of the computed function and its innate properties it could
not change it or affect it in any way.

>>>>

The early formalization of the process of computing using Turing
machines~\cite{Turing_1937,blum2012complexity} or the
$\lambda$-calculus~\cite{Church1932,Barendregt:Lambda} viewed a computation as
realizing a mathematical function. From our perspective, the most
important consequence of this view is that the properties of the
computed function existed independently of any observation,
calculation, or interaction. For example, a function is
\emph{injective} or not independently of any observation. An agent can
only interact with the computation by asking questions regarding its
input-output behavior and although such interaction would reveal
fragments of the computed function and its innate properties it could
not change it or affect it in any way.
